% Bibliographie

\begin{frame}[c]
  \frametitle{Bibliography}

\footnotesize
\setlength{\parindent}{-1em}
\setlength{\parskip}{0.5em}
~

\vfill
%\tcite{Paulevé11} Loïc Paulevé. PhD thesis: \textit{Modélisation, Simulation et Vérification des Grands Réseaux de Régulation Biologique}, October 2011, Nantes, France

\tcite{Paulev\'e et al. 2010} Loïc Paulevé, Morgan Magnin, and Olivier Roux. \textit{Tuning Temporal Features within the Stochastic $\pi$-Calculus}. IEEE Transactions on Software Engineering, 37(6):858-871, 2011.

%\tcite{PRM10-TCSB} Loïc Paulevé, Morgan Magnin, and Olivier Roux. \textit{Refining dynamics of gene regulatory networks in a stochastic $\pi$-calculus framework}. In Corrado Priami, Ralph-Johan Back, Ion Petre, and Erik de Vink, editors: Transactions on Computational Systems Biology XIII, volume 6575 of Lecture Notes in Computer Science, 171-191. Springer Berlin/Heidelberg, 2011.

\tcite{Paulev\'e et al. 2012} Loïc Paulevé, Morgan Magnin, and Olivier Roux. \textit{Static analysis of biological regulatory networks dynamics using abstract interpretation}. Mathematical Structures in Computer Science, in press, 2012.

%\tcite{PR10-CRAS} Loïc Paulevé and Adrien Richard. \textit{Topological Fixed Points in Boolean Networks}. Comptes Rendus de l'Académie des Sciences - Series I - Mathematics, 348(15-16):825 - 828, 2010.

\tcite{Richard et al. 2008} Adrien Richard, Jean-Paul Comet, and Gilles Bernot. \textit{R. Thomas' logical method}, 2008. Invited at Tutorials on modelling methods and tools: Modelling a genetic switch and Metabolic Networks, Spring School on Modelling Complex Biological Systems in the Context of Genomics.

%\tcite{CMSB12} Maxime Folschette, Loïc Paulevé, Katsumi Inoue, Morgan Magnin, and Olivier Roux. \textit{Concretizing the Process Hitting into Biological Regulatory Networks}. In: Computational Methods in Systems Biology, Springer, 2012.




\tcite{Ahmad et al. 2008}
Jamil Ahmad, Olivier Roux, Gilles Bernot, Jean-Paul Comet, and Adrien Richard.
\textit{Analysing formal models of genetic regulatory networks with delays.}
 International Journal of Bioinformatics Research and
  Applications (IJBRA), 4(3):240--262, 2008.

\tcite{Batt et al. 2007}
Gr{\'e}gory Batt, Ramzi~Ben Salah, and Oded Maler.
 \textit{On timed models of gene networks.}
 Springer, 2007.

\tcite{Gardner et al. 2003}
Timothy~S Gardner, Diego Di~Bernardo, David Lorenz, and James~J Collins.
 \textit{Inferring genetic networks and identifying compound mode of action
  via expression profiling.}
  Science, 301(5629):102--105, 2003.

\tcite{Guziolowski et al. 2012}
Carito Guziolowski, Aristotelis Kittas, Florian Dittmann, and Niels Grabe.
\textit{ Automatic generation of causal networks linking growth factor stimuli
  to functional cell state changes.}
 FEBS Journal, 279(18):3462--3474, 2012.

\tcite{Heiner et al. 2008}
Monika Heiner, David Gilbert, and Robin Donaldson.
 \textit{Petri nets for systems and synthetic biology.}
 Formal methods for computational systems biology, pages
  215--264. Springer, 2008.

\tcite{Mac Namara et al. 2012}
Aidan MacNamara, Camille Terfve, David Henriques, Beatriz~Pe{\~n}alver
  Bernab{\'e}, and Julio Saez-Rodriguez.
 \textit{State--time spectrum of signal transduction logic models.}
 Physical Biology, 9(4):045003, 2012.


\vfill
\Large
\begin{flushright}
  \tval{Thank you}\hspace{1cm}~
\end{flushright}
\vfill

~

\end{frame}

